---
title: "Introduction to the cpi package"
author: "Marvin N. Wright"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
set.seed(2022)
```

# Get started
The Conditional Predictive Impact (CPI) is a general test for conditional independence in supervised learning algorithms. It implements a conditional variable importance measure which can be applied to any supervised learning algorithm and loss function. 

As a first example, we calculate the CPI for a random forest on the iris data with 5-fold cross validation: 

```{r first_example}
library(mlr3)
library(mlr3learners)
library(cpi)

cpi(task = tsk("iris"), 
    learner = lrn("classif.ranger", predict_type = "prob"),
    resampling = rsmp("cv", folds = 5))
```
The result is a CPI value for each feature, i.e. how much did the loss function change when the feature was replaced with its knockoff version, with corresponding standard errors, test statistics, p-values and confidence interval. 

# Interface with mlr3
The task, learner and resampling strategy are specified with the *mlr3* package, which provides a unified interface for machine learning tasks and makes it quite easy to change these components. For example, we can change to regularized logistic regression and a simple holdout as resampling strategy:

```{r glmnet_example}
cpi(task = tsk("iris"), 
    learner = lrn("classif.glmnet", predict_type = "prob", lambda = 0.01),
    resampling = rsmp("holdout"))
```

We refer to [the mlr3 book](https://mlr3book.mlr-org.com/) for full introduction and reference. 

The loss function used by the `cpi()` function is specified with `measure`. By default, the mean squared error (MSE) is used for regression and log-loss for classification. In *mlr3*, this corresponds to the measures `"regr.mse"` and `"classif.logloss"`. We re-run the example above with simple classification error (ce): 

```{r glmnet_example_ce}
cpi(task = tsk("iris"), 
    learner = lrn("classif.glmnet", lambda = 0.01),
    resampling = rsmp("holdout"), 
    measure = msr("classif.ce"))
```

Note that here we do not need `predict_type = "prob"` because the classification error uses only the hard classification. 

# Statistical testing
The CPI offers several statistical tests to be calculated: The *t*-test (`"t"`, default), Wilcoxon signed-rank test (`"wilcox"`), binomial test (`"binom"`), Fisher permutation test (`"fisher"`) and Bayesian testing (`"bayes"`) with the package *BEST*. For example, we re-run the first example with Fisher's permutation test:

```{r first_example_fisher}
cpi(task = tsk("iris"), 
    learner = lrn("classif.ranger", predict_type = "prob"),
    resampling = rsmp("cv", folds = 5), 
    test = "fisher")
```

# Knockoff procedures
The CPI relies on a valid knockoff sampler for the data to be analyzed. By default, second-order Gaussian knockoffs from the package *knockoff* are used. However, any other knockoff sampler can be used by changing the `knockoff_fun` or the `x_tilde` argument in the `cpi()` function. Here, `knockoff_fun` expects a function taking a `data.frame` with the original data as input and returning a `data.frame` with the knockoffs. For example, we use sequential knockoffs from the *seqknockoff* package^[*seqknockoff* is not on CRAN yet; available here: https://github.com/kormama1/seqknockoff]: 

```{r example_seqknockoff, eval=FALSE}
mytask <- as_task_regr(iris, target = "Petal.Length")
cpi(task = mytask, learner = lrn("regr.ranger"), 
    resampling = rsmp("holdout"), 
    knockoff_fun = seqknockoff::knockoffs_seq)
```

The `x_tilde` argument directly takes the knockoff data: 
```{r example_seqknockoff_xtilde, eval=FALSE}
library(seqknockoff)
x_tilde <- knockoffs_seq(iris[, -3])
mytask <- as_task_regr(iris, target = "Petal.Length")
cpi(task = mytask, learner = lrn("regr.ranger"), 
    resampling = rsmp("holdout"), 
    x_tilde = x_tilde)
```

# Group CPI
Instead of calculating the CPI for each feature separately, we can also calculate it for groups of features by replacing data of whole groups with the respective knockoff data. In `cpi()` this can be done with the `groups` argument: 

```{r glmnet_example_group}
cpi(task = tsk("iris"), 
    learner = lrn("classif.glmnet", predict_type = "prob", lambda = 0.01),
    resampling = rsmp("holdout"), 
    groups = list(Sepal = 1:2, Petal = 3:4))
```

# Parallelization
For parallel execution, we need to register a parallel backend. Parallelization will be performed by the features, i.e. the CPI for each feature will be calculated in parallel. For example:
```{r first_example_parallel, eval=FALSE}
doParallel::registerDoParallel(4)
cpi(task = tsk("iris"), 
    learner = lrn("classif.ranger", predict_type = "prob"),
    resampling = rsmp("cv", folds = 5))
```

